<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Position and normalized expression of Fantom's tss}
-->

Position and normalized expression of Fantom's tss
========================================================

Charles Joly Beauparlant

This package and the underlying metagene code are distributed under 
the Artistic license 2.0. You are free to use and redistribute this software. 

## Installation

TODO

## Loading the library

```{r loadLibrary}
library("FantomTSS.hg19")
```

## Main functions

### `get_tss`

The `get_tss` functions returns a `GRanges` object with all the tss and no metadata columns:

```
get_tss()
```

### `get_tss_tpm`

The `get_tss_tpm` returns a `GRanges` object with all the tss and selected metadata columns:

To get the expression of tss in A549:
```{r getA546}
get_tss_tpm(cell_lines = "A549")
```

To get the expression of tss in A549 and K562:
```{r getA546K562}
get_tss_tpm(cell_lines = c("A549", "K562"))
```

To merge all the columns for a cell line by calculating the mean value for each tss:
```{r funMean}
get_tss_tpm(cell_lines = c("A549", "K562"), merge.FUN = mean)
```

To merge all the columns for a cell line by calculating the sum for each tss:
```{r funSum}
get_tss_tpm(cell_lines = c("A549", "K562"), merge.FUN = sum)
```

It's also possible to create our own function, as long as it take a `vector` of `numeric` as input and outputs a single `numeric` value:
```{r dummyFunction}
# We create a dummy function that returns first element of a vector
dummy_function <- function(x) {
  x[1]
}
get_tss_tpm(cell_lines = c("A549", "K562"), merge.FUN = dummy_function)
```
